Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-26 robdml.tex
tex

Specifically, we (adversarially) train imagenet-initialized ResNet-18
(RN18)~\cite{resnet} with the output dimension of the last layer changed to
$N{=}512$.
%
The margin $\gamma$ in triplet loss is $0.2$, which is consistent to standard
DML~\cite{revisiting}.
%
Adam~\cite{adam} optimizer is used for parameter updates, with a learning rate
as $1.0{\times}10^{-3}$ for $150$ epochs, and a mini-batch size of $112$.
%
Adversarial examples are created under the perturbation budget
$\varepsilon{=}8/255$ in infinity norm, using PGD~\cite{madry} with step size
$\alpha{=}1/255$ and a default maximum step number $\eta{=}8$.
%
The parameter $u$ is equal to $\gamma$, much less than the upperbound of the
loss function, in order to avoid excessive hardness boost in pseudo-hardness
functions $g_\mathsf{B}$ and $g_\mathsf{LGA}$.

>>>>

Specifically, we (adversarially) train imagenet-initialized ResNet-18
(RN18)~\cite{resnet} with the output dimension of the last layer changed to
$N{=}512$.
%
The margin $\gamma$ in triplet loss is $0.2$, which is consistent to standard
DML~\cite{revisiting}.
%
Adam~\cite{adam} optimizer is used for parameter updates, with a learning rate
as $1.0{\times}10^{-3}$ for $150$ epochs, and a mini-batch size of $112$.
%
Adversarial examples are created under the perturbation budget
$\varepsilon{=}8/255$ in infinity norm, using PGD~\cite{madry} with step size
$\alpha{=}1/255$ and a default maximum step number $\eta{=}8$.
%
The parameter $u$ is equal to $\gamma$, much less than the loss upperbound,
in order to avoid excessive hardness boost in $g_\mathsf{B}$ and $g_\mathsf{LGA}$.
%
Parameter $\lambda$ in $L_\text{ICS}$ is $0.5$ by default.
